My title

### 2022-02-24 outputs/paper/paper.Rmd
first commit

```{r bills, fig.cap="Bills of penguins", echo = FALSE}
f1 <- read.csv("fig_1.csv")
ggplot(f1, aes(x = year, y=brate_all)) +
  geom_point() +
  geom_line() +
  labs(y="Births per 1,000 women age 15–44") +
  theme_minimal() +

>>>>

```{r bills, fig.cap="Bills of penguins", echo = FALSE}
# Replication of Figure 1
f1 <- read.csv("fig_1.csv")
ggplot(f1, aes(x = year, y=brate_all)) +
  geom_point() +
  geom_line() +
  labs(y="Births per 1,000 women age 15–44") +
  theme_minimal() +
